\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
Updated method application example

\section{Method Application Example}

>>>>

\section{Method Application Example}
In this section, we present a mobile eye-tracking study with an educational robot Thymio II. The study exemplifies one of the use cases of the mobile eye-tracking. One part of the target (the robot) was moving, whereas the rest of the maze (or playground, figure~\ref{playground}, as we refer to it in the rest of this paper) was stationary. The participants were allowed to move but most of them remained seated for the duration of the experiment. For the purpose of the eye-tracking data analysis, we used the proportions of fixations on different  area of interest on the playground.
